---
title: "Government Compensation in California by County and Department"
author: "Moises Evangelista"
date: "July 24, 2015"
output: slidy_presentation
---

## Data source and analysis

This presentation uses data from the  California State Controller's Office, Controller Betty T. Yee.  These data can be accessed [here](http://publicpay.ca.gov/Reports/RawExport.aspx). 

The government employee wages data was put out after some government employees were being paid extremely high wages.  Information about one of these events can be found [here](https://en.wikipedia.org/wiki/City_of_Bell_scandal).



## Data analysis

- For this analysis, the data was downloaded
- Median total wages and overtime pay was calculated by county and department
- The resulting data was visualized on a graph

## How to use the application

The application can be accessed [here](https://coquito77.shinyapps.io/DevelopingDataProducts)

On the data application, select the county  of interest from the dropdown.  The graph will update based on the selection made. 

The highest total wage for the county selected and the department with the highest total wage will also update.  

In addition, the total overtime wage and the department with the highest overtime wage will also update.

## Highest total wages and total overtime pay {.smaller}

```{r include=FALSE}

setwd("C:/Users/E551910/Desktop/DevelopingDataProducts/DevelopingDataProducts/")

dataset <-  read.csv(file="./data/summarydata.txt", sep="\t",head=TRUE)

dataset$EntityName[which.max(dataset$medianTotalPay)]

library(dplyr)

highestTotalWages <- tbl_df(dataset) %>%
  filter(count  >= 30) %>%
  top_n(3, medianTotalPay)  %>%
  arrange(desc(medianTotalPay)) %>%
  select(County = EntityName, Department= DepartmentSubdivision, "Median total pay" = medianTotalPay)

highestWagesOT <- tbl_df(dataset) %>%
  filter(count  >= 30) %>%
  top_n(3, medianOT)  %>%
  arrange(desc(medianOT)) %>%
  select(County = EntityName, Department= DepartmentSubdivision, "Median overtime pay" = medianOT)

```


```{r results='asis', echo=FALSE}

library(xtable)

print(xtable(highestTotalWages,
             digits=0, 
             caption = "Top three total wage paying departments, excludes departments with fewer than 30 employeees",  
             label="tblTopTotalWages", 
             align = "rl{4cm}r{3cm}r{3cm}"), 
caption.placement = "bottom", 
include.rownames=FALSE, 
# table.placement="t", 
type='html',
format.args = list(big.mark = ",", decimal.mark = "."),
comment=FALSE)

```
|      

|       

```{r results='asis', echo=FALSE}



print(xtable(highestWagesOT,
             digits=0, 
             caption = "Top three overtime paying departments, excludes departments with fewer than 30 employeees",  
             label="tblTopOTwages", 
             align = "rl{4cm}r{3cm}r{3cm}"), 
caption.placement = "bottom", 
include.rownames=FALSE, 
# table.placement="t", 
type='html',
format.args = list(big.mark = ",", decimal.mark = "."),
comment=FALSE)



```